Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-19 paper/paper.tex
pass

Figure~\ref{fig:rule-jboss} shows a Suricata rule that captures a
JBoss RCE attack.  The option \CodeIn{flow: established, to\_server;}
indicates that a rule match will only occur on packets that (1) flow
on an already-established connection and that (2) flow to the server
as opposed to the client. For the content options the modifiers
\CodeIn{nocase} and \CodeIn{http\_uri} indicate, respectively, that
the matching not be case sensitive and that the string should be
located at the packet field ``Request URI''. \Mar{Lucas, ``nocase''
  tambem eh considerado modificador? Isto nao eh confuso? Na secao
  4.3.4 consideramos modificadores como sinonimo para qualificador de
  campo, nao?}

@@

\subsubsection{Frequency of content modifiers.} As previously
mentioned, \percRulesWithContent\ (=26K/\numrulessuri) of Suricata
rules involve content options. Furthermore, of the 26K rules that use
content options, 13K use HTTP modifiers\Mar{@Lucas, pode dar o numero
  desconsiderando HTTP? Esta parte eh generica.}. Content modifiers
serve to indicate what part of a network packet the string mentioned
in the content option should appear. For example, the modifier
\CodeIn{http\_header} in the option \CodeIn{content: ``keep-alive'';
  http\_header} states the requirement that the string ``keep-alive''
be present in the header of the message. (A keep-alive connection
attribute indicates that a single TCP connection should remain open
for multiple HTTP requests/responses.)
Figure~\ref{fig:http-header-example} illustrates possible content
options used to match against certain strings that appear in an HTTP
message. A check (resp., cross) mark indicates a match (resp.,
unmatch).

@@

\begin{table*}[h!]
  \caption{\label{table:attacks}List of attacks.\Mar{Guilherme, por
      favor, adicione mais ataques aqui...}}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth} \\
    \midrule     
    Ping Scan \MyComment{& single} & ICMP \MyComment{& Discovers
      active hosts in a network} & \scriptsize{dsize:0; itype:8;} \\
    Black Nurse \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:3; icode:3; detection\_filter:track by\_dst, count 250, seconds 1;}\\
    Ping Flood  \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:8; icode:0; detection\_filter:track by\_src, count 30, seconds 1;}\\  
    Port Scan \MyComment{& single} & TCP \MyComment{& Discovers open ports in a host} & \scriptsize{flags: A; ack: 0;dsize: 0;} \\
    SYN Flood \MyComment{& multiple} & TCP \MyComment{& Denial of Service} & \scriptsize{flags: S,12; threshold: type both, track by\_dst, count 5000, seconds 5;}\\
    UDP Flood \MyComment{& multiple} & UDP \MyComment{& Denial of Service} & \scriptsize{fragbits:M; threshold: type both, track by\_dst, count 5000, seconds 5;} \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\subsubsection{Malicious traffic.}To reproduce the malicious traffic, we
configured an HTTP server (Apache2) in one machine and ran
Nikto2~\cite{nikto} in a different machine. We used this setup to
replay each of the attacks from Table~\ref{table:attacks}.  On each
execution, we captured the incoming traffic to the web server with
Wireshark~\cite{wireshark-net-monitor} and used the corresponding pcap
files as an input to \tname.\Mar{@Lucas, eu traduzi o que vc. falou
  para ingles. Mas, aparentemente, isto esta **inconsistente** com o
  que eh dito na Secao~\ref{attack-reproduction}. Por favor, esclareca!}

>>>>

Figure~\ref{fig:rule-jboss} shows a Suricata rule that captures a
JBoss RCE attack.  The option \CodeIn{flow: established, to\_server;}
indicates that a rule match will only occur on packets that (1) flow
on an already-established connection and that (2) flow to the server
as opposed to the client. For the content options the modifiers
\CodeIn{nocase} and \CodeIn{http\_uri} indicate, respectively, that
the matching not be case sensitive and that the string should be
located at the packet field ``Request URI''. \Mar{Lucas, ``nocase''
  tambem eh considerado modificador? Isto nao eh confuso? Na secao
  4.3.4 consideramos modificadores como sinonimo para qualificador de
  campo, nao?}\Luc{Sim, ``nocase'' define que a busca pela string nao deve ser case sensitive. Em 4.3.4 estamos considerando apenas os modificadores que definem posições/campos de pacotes http.}

@@

\subsubsection{Frequency of content modifiers.} As previously
mentioned, \percRulesWithContent\ (=26K/\numrulessuri) of Suricata
rules involve content options. Furthermore, of the 26K rules that use
content options, 13K use HTTP modifiers\Mar{@Lucas, pode dar o numero
  desconsiderando HTTP? Esta parte eh generica.}. \Luc{Posso, mas nessa função nós consideramos apenas os modificadores http.} Content modifiers
serve to indicate what part of a network packet the string mentioned
in the content option should appear. For example, the modifier
\CodeIn{http\_header} in the option \CodeIn{content: ``keep-alive'';
  http\_header} states the requirement that the string ``keep-alive''
be present in the header of the message. (A keep-alive connection
attribute indicates that a single TCP connection should remain open
for multiple HTTP requests/responses.)
Figure~\ref{fig:http-header-example} illustrates possible content
options used to match against certain strings that appear in an HTTP
message. A check (resp., cross) mark indicates a match (resp.,
unmatch).

@@

\begin{table*}[h!]
  \caption{\label{table:attacks}List of attacks.\Mar{Guilherme, por
      favor, adicione mais ataques aqui...}}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth} \\
    \midrule     
    Ping Scan \MyComment{& single} & ICMP \MyComment{& Discovers
      active hosts in a network} & \scriptsize{dsize:0; itype:8;} \\
    %%Black Nurse \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:3; icode:3; detection\_filter:track by\_dst, count 250, seconds 1;}\\
    %%Ping Flood  \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:8; icode:0; detection\_filter:track by\_src, count 30, seconds 1;}\\  
    %%Port Scan \MyComment{& single} & TCP \MyComment{& Discovers open ports in a host} & \scriptsize{flags: A; ack: 0;dsize: 0;} \\
    SYN Flood \MyComment{& multiple} & TCP \MyComment{& Denial of Service} & \scriptsize{flags: S,12; threshold: type both, track by\_dst, count 5000, seconds 5;}\\
    %%UDP Flood \MyComment{& multiple} & UDP \MyComment{& Denial of Service} & \scriptsize{fragbits:M; threshold: type both, track by\_dst, count 5000, seconds 5;} \\
    JBoss JMX Console Beanshell Exploit \MyComment{& single} & HTTP \MyComment{& Remote Code Execution} & \scriptsize{content:"/HtmlAdaptor"; nocase; http\_uri; content:"action=inspect"; nocase; http\_uri; content:"bean"; nocase; http\_uri; content:"name="; http\_uri;} \\
    WeBid Local File Inclusion \MyComment{& single} & TCP \MyComment{& Local File Inclusion} & \scriptsize{content:"GET "; depth:4; content:"/cron.php?"; http\_uri; nocase; content:"include\_path="; http\_uri; nocase; content:"../";} \\
    ColdFusion Privilege Escalation \MyComment{& single} & HTTP \MyComment{& Privilege Escalation} & \scriptsize{content:"GET"; http\_method; nocase; content:"/CFIDE/administrator"; http\_uri; nocase;} \\
    \Luc{Adicionar nome} \MyComment{& single} & HTTP \MyComment{& \Luc{Adicionar}} & \scriptsize{content:".htaccess"; nocase; http\_uri;} \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\subsubsection{Malicious traffic.}To reproduce the malicious traffic, we
configured an HTTP server (Apache2) in one machine and ran
Nikto2~\cite{nikto} in a different machine. We used this setup to
replay each of the attacks from Table~\ref{table:attacks}.  On each
execution, we captured the incoming traffic to the web server with
Wireshark~\cite{wireshark-net-monitor} and used the corresponding pcap
files as an input to \tname.\Mar{@Lucas, eu traduzi o que vc. falou
  para ingles. Mas, aparentemente, isto esta **inconsistente** com o
  que eh dito na Secao~\ref{attack-reproduction}. Por favor, esclareca!}
  \Luc{Essa descrição é referente aos ataques HTTP/TCP da tabela. O hping3 gera apenas o trafego do SYN Flood. Ambas as explicações estão corretas. Creio q a descrição da seção 5.2.1 tenha q ser movida para cá pois está explicando como capturamos o trafego malicioso. Nós executamos o Nikto e o hping3 uma unica vez para capturar com o wireshark o trafego q eles geram. O trafego produzido pelo Nikto ja inclui todos os ataques que utilizamos, nós separamos os pacotes de cada um deles manualmente utilizando o wireshark.}
